---
title: "NEISS Analysis"
author: "BIFX 552 class"
date: "9/28/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(readxl)

year<-2016

# Read in NEISS data
dat <- read_excel('../Data/NEISS-data-2016-updated-APRIL2017.xlsx') %>%
       mutate(age = ifelse(age > 200, (age - 200) / 12, age), # age > 200 is coded in months since birth + 200
              male = ifelse(sex > 0, sex == 1, NA)) # 1 = Male, 2 = Female, 0 = Unknown
```

# NEISS Analysis

This is an example html file that was generated from R. This data set comes from the [Consumer Product Safety Commission](https://www.cpsc.gov/Research--Statistics), and contains data from the National Electronic Injury Surveillance System (NEISS). For more information on codes, see the [NEISS Coding Manual](https://www.cpsc.gov/s3fs-public/2017NEISSCodingManualCPSConlyNontrauma.pdf). It is important to note, for example, that a child aged nine months will have an age code of 209. You might find some of the ages suspicious if you didn't know that.

## 6-year-olds with arm injuries


# Males
```{r males, echo=FALSE}
#echo=FALSE means that none of this code will show in the final product
n6yoM<- {filter(dat, age==6 & male & 
                 body_part %in% c(33, 80)) %>% #%in% means look in body_part for either 33 or 80 
      dim()}[1] #run everything between the curly braces then give us the number of rows

#this is another way of doing the same thing
n6yoM<- filter(dat, age==6 & male & 
                 body_part %in% c(33,80))[[1]] %>% length() #[[1]] this indexes and grabs the first column of the data frame dat, doesn't matter which column b/c we just need to know the length of it.

#yet another way of doing the same thing
n6yoM<- with(dat, age==6 & male & #with says take this data frame and if you don't recognize the variable name, look within the data frame.
                 body_part %in% c(33, 80)) %>% sum()

```
There were `r n6yoM` 6yo males who were captured in the NEISS dataset in `r year`.

# Females

# Discussion
